Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-06-13 emsoft-2019/V2/response.tex

\Mahmoud{\section{Revision Letter}	
We thank the reviewers for the detailed and useful feedback on our submission. First, we will detail the main changes we made. Afterwards, we provide responses to your specific questions. 
\subsection{Changes}
We have improved our paper while considering all the minor comments. Particularly, \autoref{fig:overview} is updated and the Remark \ref{rem:eps_Q} is added. Other changes are minor and are highlighted within the body of the paper. We also plan to distribute our tool once the double blinded review phase is passed.

@@

\textbf{Taking uncertainties other than quantization into account} (Reviewer 1)\\
Our formulation is general enough to take the effect of measurement/process noise into account. More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources. However, this is not subject of study of the current paper.\\
\textbf{Complexity of the proposed approach} (Reviewer 2)\\
In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}. In theory one cannot find an upper bound for the maximum number of hyperplanes enclosing a region. To compute the incorrect region selection error, assuming that each partition at most has $\bar n_f$ faces, in the worst case $i\times\bar n_f\times 2^q$ affine computations would be enough, where $i$ denotes the number of times that RMPC design is repeated for updated $\Delta$s. In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks. \underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}\\

@@

\textbf{Releasing the developed package} (Reviewers 3 $\&$ 4)\\
We definitely plan to distribute our package once the double blinded review phase is passed.\\ 
\textbf{Reason for the special format of solution to \autoref{eq:RMPC_prob} as polyhedral decomposition} (Reviewer 3)\\
We use the results in \cite{delaPea:2005}; since this is not among this paper's contributions, we do not go beyond giving a general outline of these results.

### 2019-06-13 emsoft-2019/V2/intro.tex
updates

One way to tackle these problems is through \emph{explicit MPC} (EMPC) \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
problem but computes offline a symbolic representation of the solution as a function of the state.
At run-time, the solution is evaluated on the current state as in conventional control.
For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
using multi-parametric programming techniques.
The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
and an affine map for each region. 
\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.

>>>>

One way to tackle these problems is through \emph{explicit MPC} (EMPC) \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
problem but computes offline a symbolic representation of the solution as a function of the state.
At run-time, the solution is evaluated on the current state as in conventional control.
For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
using multi-parametric programming techniques.
The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
and an affine map for each region. 
\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{massive online computations}
or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.
